---
title: "Hofstede Cultural Value"
author: "JMJ"
date: "11/27/2020"
output: html_document
---

##Install the packages

```{r message=FALSE, warning=FALSE}
#install.packages("psych")
#install.packages("car") #car: Companion to Applied Regression
#install.packages(lmtest)
#install.packages("MASS")
#install.packages("caret")
#install.packages("foreign")
#install.packages("stargazer")
#install.packages("sandwich")
#install.packages("tidyverse")
#install.packages("ggthemes")
#install.packages("readxl")
#install.packages("ggrepel")
#install.packages('GGally')

library(psych)
library(car)
library(lmtest)
library(MASS)
library(caret)
library(foreign)
library(stargazer)
library(sandwich)

library(tidyverse) # upload the package
library(ggthemes)
library(readxl)
library(ggrepel)
library(GGally)
```

# Read cv file
```{r Descriptive Stat, message=FALSE, warning=FALSE}
cv <- read_excel("6-dimensions-for-website-2015-12-08-0-100.xls")
class(cv)

summary(cv)
head(cv)
mean(cv$idv, na.rm = TRUE)
```

## Plot

```{r simple plot, message=FALSE, warning=FALSE}
plot(cv$idv, cv$pdi)

ggplot(data=cv, aes(x=idv, y=pdi)) +
  geom_point(size=5, col='red') +
  geom_smooth(method = lm) +
  theme_wsj()

```

```{r plot with labels, message=FALSE, warning=FALSE}

#install.packages("ggrepel")
library(ggrepel)
cv %>% 
  ggplot(aes(x=idv, y=pdi))+
  geom_point(size=3, color='red')+ #cheatsheet: https://rstudio.com/wp-content/uploads/2015/12/ggplot2-cheatsheet-2.0.pdf
  geom_smooth(method = lm) +
  geom_label_repel(aes(label=ctr))
```



## Regression
```{r simple regression, message=FALSE, warning=FALSE}
lm <- lm(pdi ~ idv, data = cv)
summary(lm)
```
# Correlation
```{r Correlations, message=FALSE, warning=FALSE}
#install.packages('GGally')
library(GGally)

ggpairs(cv, columns = c(4, 3, 5, 6, 7, 8))
help("ggpairs")

ggpairs(cv %>% select(idv, pdi, mas, uai, ltowvs, ivr))

ggcorr(cv %>% select(idv, pdi, mas, uai, ltowvs, ivr))

```
## Multiple Regression

```{r Multiple Regression, message=FALSE, warning=FALSE}

mlm <- lm(ivr ~ pdi + mas + uai + ltowvs + idv, data=cv)
mlm
summary(mlm)

```
# New dataset: 

1. covid data were from WHO as of December 20, 2020, supplemented by Hong Kong and Taiwan data from https://github.com/CSSEGISandData/COVID-19
2. population data were based on esitates made on July 2020; 
3. GPD (US$million) from  "World Economic Outlook Database, October 2020". IMF.org. International Monetary Fund. 13 October 2020. Retrieved 13 October 2020.
4. Cultural value scores from Hostede's website added on Dec. 30, 2020
```{r sample size}
# n-5-1 = df = 59 --> n = 59+6 = 65. + 25 = 90
(25/65) # 38% increase in sample size

```

# Read cv.new file
```{r Descriptive Stat, message=FALSE, warning=FALSE}
cv.new <- read_excel("6-dimensions-for-website-2020-12-30-cov19.xls")
class(cv.new)

summary(cv.new)
head(cv.new)
mean(cv.new$idv, na.rm = TRUE)
```

## Plotting with new data

```{r simple plot, message=FALSE, warning=FALSE}
plot(cv.new$idv, cv.new$pdi)

ggplot(data=cv.new, aes(x=idv, y=pdi)) +
  geom_point(size=5, col='red') +
  geom_smooth(method = lm) +
  theme_wsj()

```

```{r plot with labels, message=FALSE, warning=FALSE}

#install.packages("ggrepel")
#library(ggrepel)
cv.new %>% 
  ggplot(aes(x=idv, y=pdi))+
  geom_point(size=3, color='red')+ #cheatsheet: https://rstudio.com/wp-content/uploads/2015/12/ggplot2-cheatsheet-2.0.pdf
  geom_smooth(method = lm) +
  geom_label_repel(aes(label=ctr))
```



## Regression with new data with Cultural values
```{r simple regression, message=FALSE, warning=FALSE}
lm.new <- lm(pdi ~ idv, data = cv.new)
summary(lm.new)
```
# Correlation with new data
```{r Correlations, message=FALSE, warning=FALSE}
#install.packages('GGally')
#library(GGally)

ggpairs(cv.new, columns = c(4, 3, 5, 6, 7, 8))
ggcorr(cv.new %>% select(idv, pdi, mas, uai, ltowvs, ivr))

```
## Multiple Regression with new data

```{r Multiple Regression, message=FALSE, warning=FALSE}

mlm.new <- lm(ivr ~ idv + pdi + mas + uai + ltowvs, data=cv.new)
mlm.new
summary(mlm.new)

```
#Visualizing covid data

# Covid data descriptive statistics and Data Visualization
```{r data viz with new data}
summary(cv.new)
#install.packages("psych")
#library(psych)
#help("describe")

describe(cv.new$idv)
plot(cv.new$case)

describe(cv.new$idv, trim = .05, quant = c(.1, .25, .5, .75, .90))

plot(cv.new$idv, cv.new$case)


describe(cv.new$case, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(cv.new$case)
hist(log(cv.new$case))
cv.new$lcase <- log(cv.new$case)
hist(cv.new$lcase)
describe(cv.new$lcase, trim = .05, quant = c(.1, .25, .5, .75, .90))

describe(cv.new$death, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(cv.new$death)
hist(log(cv.new$death))
cv.new$ldeath <- log(cv.new$death)
hist(cv.new$ldeath)
describe(cv.new$ldeath, trim = .05, quant = c(.1, .25, .5, .75, .90))

hist(cv.new$pop)
hist(log(cv.new$pop))
cv.new$lpop <- log(cv.new$pop)
hist(cv.new$lpop)

hist(cv.new$gdp)
hist(log(cv.new$gdp))
describe(log(cv.new$gdp), trim = .05, quant = c(.1, .25, .5, .75, .90))
cv.new$lgdp <- log(cv.new$gdp)
hist(cv.new$lgdp)

describe(cv.new$gdp, trim = .05, quant = c(.1, .25, .5, .75, .90))
summary(cv.new$gdp*1000000 / cv.new$pop)
cv.new$gdp_pc <- (cv.new$gdp*1000000) / cv.new$pop
describe(cv.new$gdp_pc, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(cv.new$gdp_pc)
hist(log(cv.new$gdp_pc))
cv.new$lgdp_pc <- log(cv.new$gdp_pc)
describe(cv.new$lgdp_pc, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(cv.new$lgdp_pc)
#cv.new$gpd_pc <- NULL

#cpp: case per population x 1,000,000
cv.new$cpp <- (cv.new$case/cv.new$pop)*1000000
cv.new[c("ctr","cpp")]
hist(cv.new$cpp)
hist(log(cv.new$cpp))

#dpp: death per population x 1,000,000
describe(cv.new$death/cv.new$pop*1000000)
cv.new$dpp <- (cv.new$death/cv.new$pop)*1000000
describe(cv.new$dpp)
hist(cv.new$dpp)
hist(log(cv.new$dpp))
describe(log(cv.new$dpp))
```

## Cultural value: descriptive statistics and Data Visualization
```{r Cultural value viz with new data}
summary(cv.new)
attach(cv.new)

describe(idv, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(idv)

describe(pdi, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(pdi)

describe(mas, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(mas)

describe(uai, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(uai)

describe(ltowvs, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(ltowvs)

describe(ivr, trim = .05, quant = c(.1, .25, .5, .75, .90))
hist(ivr)

```


```{r Correlations with new data, message=FALSE, warning=FALSE}
## Correlations
ggpairs(cv.new %>% select(cpp,dpp,lcase,ldeath,lpop,lgdp,lgdp_pc,idv,pdi,mas,uai,ltowvs,ivr))
 

```

# Regression Assumptions (https://rpubs.com/aryn999/LinearRegressionAssumptionsAndDiagnosticsInR)

## 1. Linearity (Correct functional form): Check:

Detection:
 (1) plot of y vs. x or 
 (2) plot of residuals vs. x or 
 (3) plot of Residuals vs. fitted.values

Remedy: use correct functional form

```{r Linearity: case vs. cpp}
attach(cv.new)
# case vs. idv
#(1) plot of y vs. x 
fit.case1 <- lm(case~idv)
plot(idv,case)
abline(fit.case1, col="red")

#(2) plot of residuals vs. x 
plot(fit.case1$model$idv,fit.case1$residuals)
abline(h = 0, col="blue")

#(3) plot of Residuals vs. fitted.values 
plot(fit.case1$fitted.values, fit.case1$residuals)
abline(h = 0, col="red")

plot(fit.case1, 1)

# cpp vs. idv
#(1) plot of y vs. x 
fit.cpp1 <- lm(cpp~idv)
plot(idv,cpp)
abline(fit.cpp1, col="red")

#(2) plot of residuals vs. x 
plot(fit.cpp1$model$idv,fit.cpp1$residuals)
abline(h = 0, col="blue")

#(3) plot of Residuals vs. fitted.values 
plot(fit.cpp1$fitted.values, fit.cpp1$residuals)
abline(h = 0, col="red")

plot(fit.cpp1, 1)

```


## 2. Constant Error terms  (e.g., expenditure as a function of income): Check:
Detection:
 (1) plot of y vs. x or 
 (2) plot of residuals vs. x or 
 (3) plot of Residuals vs. fitted.values
 (4) ncvTest()
 (5) BP instaTest
Remedies: 
(1) white's standard errors (https://www.r-econometrics.com/methods/hcrobusterrors/), 
(2) WLS, 
(3) Log transformation

```{r non-constant variance test}
# (4) ncvTest() # car package: H0: constant variance = Homoskedasticity
ncvTest(fit.case1) # p < .001 --> hetero
ncvTest(fit.cpp1) # p > .10 --> homo

# (5) BP (Breusch-Pagan) Test:bptest() within lmtest package: H0: constant variance = Homoskedasticity
bptest(fit.case1) # p < .05 --> Hetero
bptest(fit.cpp1) # p > .10 --> homo


```



## 3. Independet error terms: 
usually okay in cross-sectional data

Detection: (1) Durbin Watson Test for Autocorrelation

```{r Durbin Watson Test for Autocorrelation}
# (1) Durbin Watson Test for Autocorrelation: from car package
#H0: There is no autocorrelation
durbinWatsonTest(fit.case1) # p > .10 --> no autocorrelation
durbinWatsonTest(fit.cpp1) # p > .10 --> no autocorrelation
```


## 4. Normality of error terms: Check:
Issue: when the assumption is violated, the model is okay as long as N is large; when n is small, se is affected.

Detection Method:
(1) plot of y vs. x or 
(2) plot of residuals vs. x or 
(3) plot of Residuals vs. fitted.values
(4) Histogram or
(5) Q-Q plot
(6) Shapiro-Wilk Test

Remedies: change functional form?

```{r}
#(4) Histogram 
hist(fit.case1$residuals)
describe(fit.case1$residuals, trim = .05, quant = c(.1, .25, .5, .75, .90))

hist(fit.cpp1$residuals)
describe(fit.cpp1$residuals, trim = .05, quant = c(.1, .25, .5, .75, .90))

#(5) Q-Q plot
plot(fit.case1, 2)
plot(fit.cpp1, 2)

#(6) Shapiro-Wilk Normality: H0: normal distribution; studres() from MASS package

studres(fit.case1)
shapiro.test(studres(fit.case1)) # p < .001 --> res. not normally distribute

studres(fit.cpp1)
shapiro.test(studres(fit.cpp1)) # p < .001 --> res. not normally distribute

```


## 5. No multicollinearity
Issue: high correlation among X variables: expected value of X1 on y, holding X2 constant doesn't make sense.

Detection:
(1) Examine correlations between X variables (Rho ~ 1)
(2) Examine VIF

Remedies: Remove one of the variables


```{r Multicollinearity, message=FALSE, echo=FALSE}
#(1) Examine correlations between X variables (Rho ~ 1)
ggpairs(cv.new %>% select(cpp, idv, pdi, mas, uai, ltowvs, ivr, lgdp_pc, lgdp, lpop))

#(2) Examine VIF
summary(lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lgdp + lpop))
fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lgdp)
vif(fit.cpp8)
summary(fit.cpp8)

fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lpop)
vif(fit.cpp8)
summary(fit.cpp8)

```


## 6. Exogeneity
Detection:
(1) Intuition <- lit review

# Modeling with new variables
## Regressing cpp on cultgural values + pop + gdp

fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lpop)
vif(fit.cpp8)
summary(fit.cpp8)

```{r}
#Model 1
summary(lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lgdp + lpop))

#Model 2: Adj. R2 = .34
fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lgdp)
vif(fit.cpp8)
summary(fit.cpp8)
fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lgdp)
#bptest(fit.cpp8)
## Robust standard errors
  fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lgdp) 
  coeftest(fit.cpp8, vcov=vcovHC) # from lmtest package
  stargazer(fit.cpp8, coeftest(fit.cpp8, vcov=vcovHC), type = 'text')
 
#Model 3: Adj. R2 = .34
fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lpop)
vif(fit.cpp8)
summary(fit.cpp8)
fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lpop)
bptest(fit.cpp8)

## Robust standard errors
  fit.cpp8 <- lm(data = cv.new, cpp ~ idv + pdi + mas + uai + ltowvs + ivr + lgdp_pc + lpop)
  coeftest(fit.cpp8, vcov=vcovHC) # from lmtest package
  stargazer(fit.cpp8, coeftest(fit.cpp8, vcov=vcovHC), type = 'text')
```

